---
title: "Genetics-based Environmental Niche Modeling"
output: 
html_document: 
keep_md: yes

---

# Data Summary

```{r data-prev, echo = FALSE}

loadd(Data)
head(Data)
table(Data[, "ant.species"])

```

```{r map-picea, echo = FALSE}

map_occurrences(Data[Data[, "ant.species"] == "picea", ], 
                range(Data[Data[, "ant.species"] == "picea", "longitude"]), 
                range(Data[Data[, "ant.species"] == "picea", "latitude"]), 
                title = "A. picea Presence") 
                

```

# Results Summary


# Analysis and Results


## Input/Outputs




## Dependencies


## Load Data

- Use datasets HF147-12 and HF147-15 
- Data are hosted by the Environmental Data Initiative and the HF Archive
- EDI has an API for R !(EDIutils)[https://github.com/EDIorg/EDIutils]
- Data from HF archive can be sourced with URL, this is less desirable
  as URLS could change
- Make sure to remove duplicated rows (see `unique()`)
- Relevant species are:
  - *Aphaenogaster picea*
  - *A. fulva*
  - *A. tenneseensis*
  - *A. treatae*
  - *A. rudis*
  - aphNA = un-assignable specimens
